A Survey of Possible Exoskeleton Control Architectures and Algorithms\\ (Draft 2.1)

### 2015-09-20 control.tex
more updates

\section{Recommended Control Architecture}

@@

@@

>>>>

\section{Recommended Control Architecture}
\label{sec:architecture}

@@

[SOMETHING ABOUT MODELING HUMAN + EXOSKELETON + WORLD ]

@@

1) We recommend a particular control 
overall architecture in Section~\ref{sec:architecture}.

2) We recommend the use of dynamic models of the exoskeleton, as has been done
for the last decade starting with the BLEEX exoskeleton.

3) We recommend using online optimization as part of the Lowest Level Controller
in the form of Quadratic Programming. This was tested by the top biped robot
teams in the DARPA Robotics Challenge, and worked well.

4) We recommend applying as many sensors as possible, and asking the performers
to make it easy to add more by making the sensor network available in the design.
This maximizes the probability of success
with respect to control architectures and algorithms by enabling multiple control
approaches to be implemented, refined, and support each other.
In particular, we would like to see force sensing between the operator and the
exoskeleton, including at the feet, as much force sensing between the exoskeleton 
and the world as possible, but minimally full six-axis force/torque sensing at
the exoskeleton feet (where they touch the ground). We would like to see multiple MEMs
IMUs (measuring linear acceleration and angular velocity) installed across 
the exoskeleton. We would like to see high quality direct velocity sensing
such as high count (100,000 counts/revolution) rotary encoders and 
analog linear tachometers.

5) {\bf Controversial:} We recommend a ``symbiotic'' control system design,
which expects the operator to adapt to the exoskeleton and its control,
and which has the control customized for the operator.
